# Colombia


```{r}
#| label: Colombia-loading
#| include: false
source("R/load-all.r")
colombia_lyrs <- country_map_lyrs("Colombia")
```

## Project-856
This project is the only one for which reproducible code was provided. We 
therefore assume that the selected donors match those used in the publication. 
The number of donors and the size of the donor pool match exactly what is 
reported in *Table A9* of the supplementary materials. However, the locations 
appear not to match those in *Fig. S4.*.

```{r}
#| label: fig-Colombia-856-sc
#| fig-cap:  !expr paste0("Colombia-Project-856 synthetic control; comprising ", proj_856_count$n_weighted, " donors from a potential pool of ", proj_856_count$n_pot, " donors. The donor pool subset is based on a buffer deforestation threshold value of ", proj_856_donors_l$cutoff)
#| echo: false
#| message: false
#| warning: false
#| results: hide
project_856 <- west_extract_proj_area(colombia_lyrs$country_sc_sp, 856)
proj_856_donors_l <- sc_wrap_recursive(
  filepath = colombia_lyrs$country_csv,
  dbf_file = colombia_lyrs$country_dbf,
  project_id = 856,
  project_start_date = 2011,
  project_name = "Colombia 856",
  drop_controls = c(8851),
  cutoff_start = 0.2,
  predictors_list = c(
    "tree", "IL", "pa", "slope", "dem", "fric", "def",
    "defc", "mm", "buf10k_def", "buf10k_defc"
  )
)

proj_856_count <- count_donors(proj_856_donors_l)

proj_856_donors <- proj_856_donors_l |>
  locate_donors(colombia_lyrs$country_sc_sp)
```
```{r}
#| label: fig-Colombia-856-map
#| fig-cap: "Colombia-Project-856 synthetic control map"
#| echo: false
#| message: false
#| warning: false
donor_leaf_map(proj_donors=proj_856_donors, 
  country_spat = colombia_lyrs$country,
  country_name = "Colombia",
  project_area = project_856,
  proj_num = 856,
  ecoregions=colombia_lyrs$ecoregions,
  states = colombia_lyrs$states)

```

## Project-1390
This SC matches that of the paper.
```{r}
#| label: fig-Colombia-1390
#| fig-cap: !expr paste0("Colombia-Project-1390 synthetic control; comprising ", proj_1390_count$n_weighted, " donors from a potential pool of ", proj_1390_count$n_pot, " donors. The donor pool subset is based on a buffer deforestation threshold value of ", proj_1390_donors_l$cutoff)
#| echo: false
#| message: false
#| warning: false
#| results: hide

project_1390 <- west_extract_proj_area(colombia_lyrs$country_sc_sp, 1390)

proj_1390_donors_l <- sc_wrap_recursive(
  filepath = colombia_lyrs$country_csv,
  dbf_file = colombia_lyrs$country_dbf,
  project_id = 1390,
  project_start_date = 2013,
  project_name = "Colombia 1390",
  predictors_list = c(
    "tree", "IL", "pa", "slope", "dem", "palm", "mine", "fric", "def",
    "defc", "mm", "buf10k_def", "buf10k_defc"
  ),
  drop_controls = c() 
)

proj_1390_count <- count_donors(proj_1390_donors_l)

proj_1390_donors <- proj_1390_donors_l |>
  locate_donors(colombia_lyrs$country_sc_sp)
```
```{r}
#| label: fig-Colombia-1390-map
#| fig-cap: "Colombia-Project-1390 synthetic control map"
#| echo: false
#| message: false
#| warning: false

donor_leaf_map(proj_donors=proj_1390_donors,
  country_spat = colombia_lyrs$country,
  country_name = "Colombia",
  project_area = project_1390,
  proj_num = 1390,
  ecoregions=colombia_lyrs$ecoregions,
  states = colombia_lyrs$states)
```


## Project-1391

```{r}
#| label: fig-Colombia-1391
#| fig-cap: !expr paste0("Colombia-Project-1391 synthetic control; comprising ", proj_1391_count$n_weighted, " donors from a potential pool of ", proj_1391_count$n_pot, " donors. The donor pool subset is based on a buffer deforestation threshold value of ", proj_1391_donors_l$cutoff)
#| echo: false
#| message: false
#| warning: false
#| results: hide

project_1391 <- west_extract_proj_area(colombia_lyrs$country_sc_sp, 1391)
proj_1391_donors_l <- sc_wrap_recursive(
  filepath = colombia_lyrs$country_csv,
  dbf_file = colombia_lyrs$country_dbf,
  project_id = 1391,
  project_start_date = 2013,
  project_name = "Colombia 1391",
  predictors_list = c(
    "tree", "IL", "pa", "slope", "dem", "palm", "mine", "fric", "def",
    "defc", "mm", "buf10k_def", "buf10k_defc"
  ),
  drop_controls = c(),
  cutoff_start = 0.3
) 

proj_1391_count <- count_donors(proj_1391_donors_l)

proj_1391_donors <- proj_1391_donors_l |>
  locate_donors(colombia_lyrs$country_sc_sp)

```
```{r}
#| label: fig-Colombia-1391-map
#| fig-cap: "Colombia-Project-1391 synthetic control map"
#| echo: false
#| message: false
#| warning: false
donor_leaf_map(proj_donors=proj_1391_donors,
  country_spat = colombia_lyrs$country,
  country_name = "Colombia",
  project_area = project_1391,
  proj_num = 1391,
  ecoregions=colombia_lyrs$ecoregions,
  states = colombia_lyrs$states)
```

## Project-1392

```{r}
#| label: fig-Colombia-1392
#| fig-cap: !expr paste0("Colombia-Project-1392 synthetic control; comprising ", proj_1392_count$n_weighted, " donors from a potential pool of ", proj_1392_count$n_pot, " donors. The donor pool subset is based on a buffer deforestation threshold value of ", proj_1392_donors_l$cutoff)
#| echo: false
#| message: false
#| warning: false
#| results: hide

project_1392 <- west_extract_proj_area(colombia_lyrs$country_sc_sp, 1392)
proj_1392_donors_l <- sc_wrap_recursive(
  filepath = colombia_lyrs$country_csv,
  dbf_file = colombia_lyrs$country_dbf,
  project_id = 1392,
  project_start_date = 2013,
  project_name = "Colombia 1392",
  predictors_list = c(
    "tree", "IL", "pa", "slope", "dem", "fric", "def",
    "defc", "mm", "buf10k_def", "buf10k_defc"
  ),
  drop_controls = c(),
  cutoff_start = 0.2
) 

proj_1392_count <- count_donors(proj_1392_donors_l)

proj_1392_donors <- proj_1392_donors_l |>
  locate_donors(colombia_lyrs$country_sc_sp)

```
```{r}
#| label: fig-Colombia-1392-map
#| fig-cap: "Colombia-Project-1392 synthetic control map"
#| echo: false
#| message: false
#| warning: false
donor_leaf_map(proj_donors=proj_1392_donors,
  country_spat = colombia_lyrs$country,
  country_name = "Colombia",
  project_area = project_1392,
  proj_num = 1392,
  ecoregions=colombia_lyrs$ecoregions,
  states = colombia_lyrs$states)
```


## Project-1395

```{r}
#| label: fig-Colombia-1395
#| fig-cap: !expr paste0("Colombia-Project-1395 synthetic control; comprising ", proj_1395_count$n_weighted, " donors from a potential pool of ", proj_1395_count$n_pot, " donors. The donor pool subset is based on a buffer deforestation threshold value of ", proj_1395_donors_l$cutoff)
#| echo: false
#| message: false
#| warning: false
#| results: hide

project_1395 <- west_extract_proj_area(colombia_lyrs$country_sc_sp, 1395)
proj_1395_donors_l <- sc_wrap_recursive(
  filepath = colombia_lyrs$country_csv,
  dbf_file = colombia_lyrs$country_dbf,
  project_id = 1395,
  project_start_date = 2013,
  project_name = "Colombia 1395",
  predictors_list = c(
    "tree", "IL", "pa", "slope", "dem", "palm", "mine", "fric", "def",
    "defc", "mm", "buf10k_def", "buf10k_defc"
  ),
  drop_controls = c() 
) 

proj_1395_count <- count_donors(proj_1395_donors_l)

proj_1395_donors <- proj_1395_donors_l |>
  locate_donors(colombia_lyrs$country_sc_sp)
```
```{r}
#| label: fig-Colombia-1395-map
#| fig-cap: "Colombia-Project-1395 synthetic control map"
#| echo: false
#| message: false
#| warning: false

donor_leaf_map(proj_donors=proj_1395_donors,
  country_spat = colombia_lyrs$country,
  country_name = "Colombia",
  project_area = project_1395,
  proj_num = 1395,
  ecoregions=colombia_lyrs$ecoregions,
  states = colombia_lyrs$states)
```

## Project-1396

```{r}
#| label: fig-Colombia-1396
#| fig-cap: !expr paste0("Colombia-Project-1396 synthetic control; comprising ", proj_1396_count$n_weighted, " donors from a potential pool of ", proj_1396_count$n_pot, " donors. The donor pool subset is based on a buffer deforestation threshold value of ", proj_1396_donors_l$cutoff)
#| echo: false
#| message: false
#| warning: false
#| results: hide

project_1396 <- west_extract_proj_area(colombia_lyrs$country_sc_sp, 1396)

proj_1396_donors_l <- sc_wrap_recursive(
  filepath = colombia_lyrs$country_csv,
  dbf_file = colombia_lyrs$country_dbf,
  project_id = 1396,
  project_start_date = 2013,
  project_name = "Colombia 1396",
  predictors_list = c(
    "tree", "IL", "pa", "slope", "dem", "palm", "mine", "fric", "def",
    "defc", "mm", "buf10k_def", "buf10k_defc"
  ),
  drop_controls = c(),
  cutoff_start = 0.2
) 

proj_1396_count <- count_donors(proj_1396_donors_l)

proj_1396_donors <- proj_1396_donors_l |>
  locate_donors(colombia_lyrs$country_sc_sp)
```
```{r}
#| label: fig-Colombia-1396-map
#| fig-cap: "Colombia-Project-1396 synthetic control map"
#| echo: false
#| message: false
#| warning: false

donor_leaf_map(proj_donors=proj_1396_donors,
  country_spat = colombia_lyrs$country,
  country_name = "Colombia",
  project_area = project_1396,
  proj_num = 1396,
  ecoregions=colombia_lyrs$ecoregions,
  states = colombia_lyrs$states)
```


## Project-1400

```{r}
#| label: fig-Colombia-1400
#| fig-cap: !expr paste0("Colombia-Project-1400 synthetic control; comprising ", proj_1400_count$n_weighted, " donors from a potential pool of ", proj_1400_count$n_pot, " donors. The donor pool subset is based on a buffer deforestation threshold value of ", proj_1400_donors_l$cutoff)
#| echo: false
#| message: false
#| warning: false
#| results: hide

project_1400 <- west_extract_proj_area(colombia_lyrs$country_sc_sp, 1400)

proj_1400_donors_l <- sc_wrap_recursive(
  filepath = colombia_lyrs$country_csv,
  dbf_file = colombia_lyrs$country_dbf,
  project_id = 1400,
  project_start_date = 2013,
  project_name = "Colombia 1400",
  predictors_list = c(
    "tree", "IL", "pa", "slope", "dem", "palm", "mine", "fric", "def",
    "defc", "mm", "buf10k_def", "buf10k_defc"
  ),
  drop_controls = c() 
) 

proj_1400_count <- count_donors(proj_1400_donors_l)

proj_1400_donors <- proj_1400_donors_l |>
  locate_donors(colombia_lyrs$country_sc_sp)
```
```{r}
#| label: fig-Colombia-1400-map
#| fig-cap: "Colombia-Project-1400 synthetic control map"
#| echo: false
#| message: false
#| warning: false

donor_leaf_map(proj_donors=proj_1400_donors,
  country_spat = colombia_lyrs$country,
  country_name = "Colombia",
  project_area = project_1400,
  proj_num = 1400,
  ecoregions=colombia_lyrs$ecoregions,
  states = colombia_lyrs$states)
```

## Project-1566

```{r}
#| label: fig-Colombia-1566
#| fig-cap: !expr paste0("Colombia-Project-1566 synthetic control; comprising ", proj_1566_count$n_weighted, " donors from a potential pool of ", proj_1566_count$n_pot, " donors. The donor pool subset is based on a buffer deforestation threshold value of ", proj_1566_donors_l$cutoff)
#| echo: false
#| message: false
#| warning: false
#| results: hide

project_1566 <- west_extract_proj_area(colombia_lyrs$country_sc_sp, 1566)

proj_1566_donors_l <- sc_wrap_recursive(
  filepath = colombia_lyrs$country_csv,
  dbf_file = colombia_lyrs$country_dbf,
  project_id = 1566,
  project_start_date = 2013,
  project_name = "Colombia 1566",
  predictors_list = c(
    "tree", "IL", "pa", "slope", "dem", "mine", "fric", "def",
    "defc", "mm", "buf10k_def", "buf10k_defc"
  ),
  drop_controls = c(),
  cutoff_start = 0.3
) 

proj_1566_count <- count_donors(proj_1566_donors_l)

proj_1566_donors <- proj_1566_donors_l |>
  locate_donors(colombia_lyrs$country_sc_sp)
```
```{r}
#| label: fig-Colombia-1566-map
#| fig-cap: "Colombia-Project-1566 synthetic control map"
#| echo: false
#| message: false
#| warning: false

donor_leaf_map(proj_donors=proj_1566_donors,
  country_spat = colombia_lyrs$country,
  country_name = "Colombia",
  project_area = project_1566,
  proj_num = 1566,
  ecoregions=colombia_lyrs$ecoregions,
  states = colombia_lyrs$states)
```
